---
title: "EDA"
author: "Group 8"
date: "11/26/2021"
output: html_document
---

```{r}
#Load libraries
library(tidyverse)
library(ggcorrplot)
```

### Load data

```{r}
accidents = read_csv('Cleaned_and_Preprocessed_Data.csv')
summary(accidents)
```

# Transformations Required

## Convert some numeric columns to Factors
```{r}
accidents = accidents %>% 
  mutate(Severity = as_factor(Severity),
         Amenity = as_factor(Amenity),
         Crossing = as_factor(Crossing),
         Junction = as_factor(Junction),
         Railway = as_factor(Railway),
         Station = as_factor(Station),
         Stop = as_factor(Stop),
         Traffic_Signal= as_factor(Traffic_Signal))

```

## Convert some character columns to Factors
```{r}
accidents = accidents %>% 
  mutate(Side = as_factor(Side),
         Sunrise_Sunset  = as_factor(Sunrise_Sunset),
         Civil_Twilight = as_factor(Civil_Twilight),
         Nautical_Twilight = as_factor(Nautical_Twilight),
         Astronomical_Twilight = as_factor(Astronomical_Twilight),
         Weather_Condition = as_factor(Weather_Condition),
         Wind_Direction = as_factor(Wind_Direction),
         Month = as_factor(Month),
         Zipcode = as_factor(Zipcode),
         State = as_factor(State),
         City = as_factor(City),
         County = as_factor(County),
         Street = as_factor(Street),)

accidents$Month = factor(accidents$Month,level = c('February','March','April','May','June','July','August','September','October','November','December'))
```

```{r}
str(accidents)
```
## Logical Groupings of Attributes
### Accidents Information:
  Numeric: Duration,Distance(mi)
  Factor: Severity, Month
### Weather information:
  Numeric: Temperature(F),Humidity(%),Pressure(in),Pressure(in),Visibility(mi),Wind_Speed(mph),Precipitation(in)
  Factor: Weather_Condition,Wind_Direction,Sunrise_Sunset,Civil_Twilight,Nautical_Twilight,Astronomical_Twilight
### Address Information:
  Factor: Street, Side, City, County, State, Zipcode   
### Road Information:
  Factor: Amenity, Crossing, Junction, Railway, Station, Stop, Traffic_Signal

# Univariate Analysis
```{r}
library(ggplot2)
library(gridExtra)
```

##  Numeric Attributes

Address Information: Duration,Distance(mi)
Weather Information: Temperature(F),Humidity(%),Pressure(in),Visibility(mi),Wind_Speed(mph),Precipitation(in)

```{r, fig.height=6, fig.width=12}
p1 = ggplot(accidents) + geom_histogram(aes(x=`Duration`))
p2 = ggplot(accidents) + geom_histogram(aes(x=`Distance(mi)`))
p3 = ggplot(accidents) + geom_histogram(aes(x=`Temperature(F)`))
p4 = ggplot(accidents) + geom_histogram(aes(x=`Humidity(%)`))
p5 = ggplot(accidents) + geom_histogram(aes(x=`Pressure(in)`))
p6 = ggplot(accidents) + geom_histogram(aes(x=`Visibility(mi)`))
p7 = ggplot(accidents) + geom_histogram(aes(x=`Wind_Speed(mph)`))
p8 = ggplot(accidents) + geom_histogram(aes(x=`Precipitation(in)`))

grid.arrange(p1, p2,nrow=1,top="Address Information")
grid.arrange(p3, p4, p5, p6, p7, p8,nrow=3,top="Weather Information")
```

Address Information: Most of Duration and Distance are very short. 
Weather Information: Looks Normal.

## Factor Attributes

Accident Information: Severity,Month
Weather Information: Wind_Direction,Weather_Condition,Sunrise_Sunset,Civil_Twilight,Nautical_Twilight,Astronomical_Twilight
Address Information: Street, Side, City, County, State, Zipcode
Road Information: Amenity, Crossing, Junction, Railway, Station, Stop, Traffic_Signal

```{r, fig.height=12, fig.width=12}
p9 = ggplot(accidents) + geom_bar(aes(x=`Month`))
p24 = ggplot(accidents) + geom_bar(aes(x=`Severity`))

p11 = ggplot(accidents) + geom_bar(aes(x=`Wind_Direction`))
p12 = ggplot(accidents) + geom_bar(aes(x=`Weather_Condition`))
p20 = ggplot(accidents) + geom_bar(aes(x=`Sunrise_Sunset`))
p21 = ggplot(accidents) + geom_bar(aes(x=`Civil_Twilight`))
p22 = ggplot(accidents) + geom_bar(aes(x=`Nautical_Twilight`))
p23 = ggplot(accidents) + geom_bar(aes(x=`Astronomical_Twilight`))

p10 = ggplot(accidents) + geom_bar(aes(x=Side))
p29 = ggplot(accidents) + geom_bar(aes(x=Street))
p25 = ggplot(accidents) + geom_bar(aes(x=County))
p26 = ggplot(accidents) + geom_bar(aes(x=City))
p27 = ggplot(accidents) + geom_bar(aes(x=State))
p28 = ggplot(accidents) + geom_bar(aes(x=Zipcode))


p13 = ggplot(accidents) + geom_bar(aes(x=`Amenity`))
p14 = ggplot(accidents) + geom_bar(aes(x=`Crossing`))
p15 = ggplot(accidents) + geom_bar(aes(x=`Junction`))
p16 = ggplot(accidents) + geom_bar(aes(x=`Railway`))
p17 = ggplot(accidents) + geom_bar(aes(x=`Station`))
p18 = ggplot(accidents) + geom_bar(aes(x=`Stop`))
p19 = ggplot(accidents) + geom_bar(aes(x=`Traffic_Signal`))


grid.arrange(p9, p24, nrow=2,top='Accident Information')
grid.arrange(p11, p12, p20, p21, p22, p23, nrow=3,top='Weather Information')
grid.arrange(p10, p25, p26, p27, p28, p29, nrow=3,top='Address Information')
grid.arrange(p13, p14, p15, p16, p17, p18, p19, nrow=4,top='Road Information')
```

```{r, fig.height=6.8, fig.width=7.2}
accidents %>%
   group_by(State) %>% 
   summarise(Count = n()) %>%
   filter(Count == max(Count))
accidents %>%
   group_by(County) %>% 
   summarise(Count = n()) %>%
   filter(Count == max(Count))
```

Accident Information: Winter and Fall has more accidents than Spring and Summer (Insight). Serverity 2 takes the most part.
Weather Information: Calm takes the most part. Cloudy and Clear takes the most part. Day has more accidents than Night.
Address Information: CA in states and Los Angeles in counties has the most occurred accidents (Insights).
Road Information: Looks Normal


```{r, fig.height=6.8, fig.width=7.2}
library(dplyr)
a1 <- accidents %>% group_by(City) %>% count() %>% arrange(-n)
a1 <- head(a1, 10)
a1$City <- factor(a1$City, levels = a1$City)
b1<- ggplot(a1) + geom_col(aes(x=City, y = n))

a1 <- accidents %>% group_by(County) %>% count() %>% arrange(-n)
a1 <- head(a1, 10)
a1$County <- factor(a1$County, levels = a1$County)
b2 <- ggplot(a1) + geom_col(aes(x=County, y = n))

a1 <- accidents %>% group_by(Street) %>% count() %>% arrange(-n)
a1 <- head(a1, 10)
a1$Street <- factor(a1$Street, levels = a1$Street)
b3 <- ggplot(a1) + geom_col(aes(x=Street, y = n))

a1 <- accidents %>% group_by(State   ) %>% count() %>% arrange(-n)
a1 <- head(a1, 10)
a1$State    <- factor(a1$State   , levels = a1$State   )
b4 <- ggplot(a1) + geom_col(aes(x=State   , y = n))

grid.arrange(b1, b2,b3,b4, nrow=2)
```


# Bivariate Analysis

## Measure/Measure

```{r, fig.height=12, fig.width=9.8}
library(GGally)
nums <- sapply(accidents, is.numeric)
d <- accidents[,nums]
#too many points for scatters
set.seed(1)
#draw a sparse plot but keep the original pattern
id <- sample(1:nrow(d), 2000)
d2 <- d[id,]
ggpairs(d2)

ggcorrplot(cor(d, use = "pairwise.complete.obs"))

```



## Category/Category
```{r,fig.height=9.8, fig.width=9.8}
cc1 = ggplot(accidents) + geom_count(aes(x= Severity, y = Month ))
cc2 = ggplot(accidents) + geom_bar(aes(x=  Severity, fill =Side )) 


cc3 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Wind_Direction ))
cc4 = ggplot(accidents) +  geom_bar(aes(x= Severity, fill =Weather_Condition  ))
cc5 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Amenity  )) 
cc6 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Crossing  )) 
cc7 = ggplot(accidents) + geom_bar(aes(x= Severity, fill =  Junction  )) 
cc8 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Railway  )) 
cc9 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Station   )) 
cc10 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Stop    )) 
cc11 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Traffic_Signal  )) 
cc12 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Sunrise_Sunset )) 
cc13 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Sunrise_Sunset )) 
cc14 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Nautical_Twilight )) 
cc15 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Civil_Twilight  )) 
cc16 = ggplot(accidents) + geom_bar(aes(x= Severity, fill = Astronomical_Twilight  ))

grid.arrange(cc2, cc3,cc4, cc5, cc6, cc7, cc8,  nrow = 3)

grid.arrange(cc9,cc10, cc11, cc12, cc13, cc14, cc15, nrow = 4)
```

### Severity vs Other Categories
```{r}
g2 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Severity), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Severity), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Severity), position = "fill") + labs(y = "Percent")
g6 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Severity), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Severity), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Severity), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Severity), position = "fill") + labs(y = "Percent")

g10 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Severity), position = "fill") + labs(y = "Percent")
g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Severity), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Severity), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Severity), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Severity), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Severity), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Severity), position = "fill") + labs(y = "Percent")

grid.arrange(g2, nrow=1,top = "Severity vs Accident Categories")
grid.arrange(g3,g5,g6,g7,g8,g9, nrow=4,top = "Severity vs Weather Categories")
grid.arrange(g10,g11,g12,g13,g14,g15,g16, nrow=4,top = "Severity vs Road Categories")
```

### Amenity vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Amenity), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Amenity), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Amenity), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Amenity), position = "fill") + labs(y = "Percent")
g6 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Amenity), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Amenity), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Amenity), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Amenity), position = "fill") + labs(y = "Percent")

g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Amenity), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Amenity), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Amenity), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Amenity), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Amenity), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Amenity), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Amenity vs Accident Categories")
grid.arrange(g3,g5,g6,g7,g8,g9, nrow=4,top = "Amenity vs Weather Categories")
grid.arrange(g11,g12,g13,g14,g15,g16, nrow=4,top = "Amenity vs Road Categories")
```

It seems Road Information vs other categories are meaningless since usually most of these road categories are false for its value. However, we will do Junction and Trafic_Signal vs other categories because these two has more balance value than other categories.

### Junction vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Junction), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Junction), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Junction), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Junction), position = "fill") + labs(y = "Percent")
g6 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Junction), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Junction), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Junction), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Junction), position = "fill") + labs(y = "Percent")

g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Junction), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Junction), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Junction), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Junction), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Junction), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Junction), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Junction vs Accident Categories")
grid.arrange(g3,g5,g6,g7,g8,g9, nrow=4,top = "Junction vs Weather Categories")
grid.arrange(g11,g12,g13,g14,g15,g16, nrow=4,top = "Junction vs Road Categories")
```

### Traffic_Signal vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g6 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")

g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Traffic_Signal), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Traffic_Signal vs Accident Categories")
grid.arrange(g3,g5,g6,g7,g8,g9, nrow=4,top = "Traffic_Signal vs Weather Categories")
grid.arrange(g11,g12,g13,g14,g15,g16, nrow=4,top = "Traffic_Signal vs Road Categories")
```


### Sunrise_Sunset vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")

g10 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Sunrise_Sunset), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Sunrise_Sunset vs Accident Categories")
grid.arrange(g3,g5,g7,g8,g9, nrow=4,top = "Sunrise_Sunset vs Weather Categories")
grid.arrange(g10,g11,g12,g13,g14,g15,g16, nrow=4,top = "Sunrise_Sunset vs Road Categories")
```

### Civil_Twilight vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")

g10 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Civil_Twilight), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Civil_Twilight vs Accident Categories")
grid.arrange(g3,g5,g7,g8,g9, nrow=4,top = "Civil_Twilight vs Weather Categories")
grid.arrange(g10,g11,g12,g13,g14,g15,g16, nrow=4,top = "Civil_Twilight vs Road Categories")
```

### Nautical_Twilight vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Astronomical_Twilight, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")

g10 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Nautical_Twilight), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Nautical_Twilight vs Accident Categories")
grid.arrange(g3,g5,g7,g8,g9, nrow=4,top = "Nautical_Twilight vs Weather Categories")
grid.arrange(g10,g11,g12,g13,g14,g15,g16, nrow=4,top = "Nautical_Twilight vs Road Categories")
```


### Astronomical_Twilight vs Other Categories
```{r}
g1 = ggplot(accidents) + geom_bar(aes(x=Month, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g2 = ggplot(accidents) + geom_bar(aes(x=Severity, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")

g3 = ggplot(accidents) + geom_bar(aes(x=Weather_Condition, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g5 = ggplot(accidents) + geom_bar(aes(x=Wind_Direction, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g7 = ggplot(accidents) + geom_bar(aes(x=Sunrise_Sunset, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g8 = ggplot(accidents) + geom_bar(aes(x=Civil_Twilight, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g9 = ggplot(accidents) + geom_bar(aes(x=Nautical_Twilight, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")

g10 = ggplot(accidents) + geom_bar(aes(x=Amenity, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g11 = ggplot(accidents) + geom_bar(aes(x=Crossing, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g12 = ggplot(accidents) + geom_bar(aes(x=Junction, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g13 = ggplot(accidents) + geom_bar(aes(x=Railway, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g14 = ggplot(accidents) + geom_bar(aes(x=Station, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g15 = ggplot(accidents) + geom_bar(aes(x=Stop, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")
g16 = ggplot(accidents) + geom_bar(aes(x=Traffic_Signal, fill = Astronomical_Twilight), position = "fill") + labs(y = "Percent")

grid.arrange(g1,g2, nrow=2,top = "Astronomical_Twilight vs Accident Categories")
grid.arrange(g3,g5,g7,g8,g9, nrow=4,top = "Astronomical_Twilight vs Weather Categories")
grid.arrange(g10,g11,g12,g13,g14,g15,g16, nrow=4,top = "Astronomical_Twilight vs Road Categories")
```
After looking at the Sunrise_Sunset,Civil_Twilight,Nautical_Twilight,Astronomical_Twilight vs other categories, it seems that the more severe accidents, the more probability they may occur in the Night.
Also, it is easy to see that Sunrise_Sunset has the looser definition for Night than the other three Civil_Twilight,Nautical_Twilight,Astronomical_Twilight (i.e. larger range for Night), which proved what we know from the resources online.
The last insight is that we could see that July usually has more accidents occurring at Day and accidents occurring in December are more probably at Night. That would comply with our knowledge, that is on Winter Night usually has more hour than Day. Summer usually has more hours at Day.

## Category/Measure

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=Duration  ))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Distance(mi)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Temperature(F)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x=Severity , y=`Humidity(%)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Pressure(in)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x=Severity , y=`Visibility(mi)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Wind_Speed(mph)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x=Severity , y=`Precipitation(in)`))

grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow = 4)
```
### Categories vs Distance(mi)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Distance(mi)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Distance(mi)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Distance(mi)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Distance(mi)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Distance(mi)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Distance(mi)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Distance(mi)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Distance(mi)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Distance(mi)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Distance(mi)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Distance(mi)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Distance(mi)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Distance(mi)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Distance(mi)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Distance(mi)`))

grid.arrange(p1,p2,nrow = 2,top='Distance(mi) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Distance(mi) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Distance(mi) vs Road categories')
```

### Category vs Duration

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=Duration))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=Duration))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=Duration))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=Duration))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=Duration))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=Duration))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=Duration))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=Duration))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=Duration))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=Duration))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=Duration))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=Duration))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=Duration))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=Duration))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=Duration))

grid.arrange(p1,p2,nrow = 2,top='Duration vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Duration vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Duration vs Road categories')
```

### Category vs Temperature(F)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Temperature(F)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Temperature(F)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Temperature(F)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Temperature(F)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Temperature(F)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Temperature(F)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Temperature(F)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Temperature(F)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Temperature(F)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Temperature(F)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Temperature(F)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Temperature(F)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Temperature(F)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Temperature(F)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Temperature(F)`))

grid.arrange(p1,p2,nrow = 2,top='Temperature(F) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Temperature(F) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Temperature(F) vs Road categories')
```

### Category vs Humidity(%)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Humidity(%)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Humidity(%)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Humidity(%)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Humidity(%)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Humidity(%)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Humidity(%)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Humidity(%)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Humidity(%)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Humidity(%)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Humidity(%)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Humidity(%)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Humidity(%)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Humidity(%)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Humidity(%)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Humidity(%)`))

grid.arrange(p1,p2,nrow = 2,top='THumidity(%) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Humidity(%) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Humidity(%) vs Road categories')
```


### Category vs Pressure(in)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Pressure(in)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Pressure(in)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Pressure(in)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Pressure(in)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Pressure(in)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Pressure(in)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Pressure(in)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Pressure(in)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Pressure(in)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Pressure(in)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Pressure(in)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Pressure(in)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Pressure(in)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Pressure(in)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Pressure(in)`))

grid.arrange(p1,p2,nrow = 2,top='Pressure(in) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Pressure(in) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Pressure(in) vs Road categories')
```

### Category vs Visibility(mi)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Visibility(mi)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Visibility(mi)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Visibility(mi)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Visibility(mi)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Visibility(mi)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Visibility(mi)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Visibility(mi)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Visibility(mi)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Visibility(mi)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Visibility(mi)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Visibility(mi)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Visibility(mi)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Visibility(mi)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Visibility(mi)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Visibility(mi)`))

grid.arrange(p1,p2,nrow = 2,top='Visibility(mi) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Visibility(mi) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Visibility(mi) vs Road categories')
```


### Category vs Wind_Speed(mph)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Wind_Speed(mph)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Wind_Speed(mph)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Wind_Speed(mph)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Wind_Speed(mph)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Wind_Speed(mph)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Wind_Speed(mph)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Wind_Speed(mph)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Wind_Speed(mph)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Wind_Speed(mph)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Wind_Speed(mph)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Wind_Speed(mph)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Wind_Speed(mph)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Wind_Speed(mph)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Wind_Speed(mph)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Wind_Speed(mph)`))

grid.arrange(p1,p2,nrow = 2,top='Wind_Speed(mph) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Wind_Speed(mph) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Wind_Speed(mph) vs Road categories')
```

### Category vs Precipitation(in)

```{r, fig.height=9.8, fig.width=6.8}
p1 <- ggplot(accidents) + geom_boxplot(aes(x= Severity , y=`Precipitation(in)`))

p2 <-ggplot(accidents) + geom_boxplot(aes(x= Month , y=`Precipitation(in)`))

p3 <-ggplot(accidents) + geom_boxplot(aes(x= Weather_Condition , y=`Precipitation(in)`))


p4 <-ggplot(accidents) + geom_boxplot(aes(x= Wind_Direction , y=`Precipitation(in)`))

p5 <-ggplot(accidents) + geom_boxplot(aes(x= Sunrise_Sunset , y=`Precipitation(in)`))

p6 <-ggplot(accidents) + geom_boxplot(aes(x= Civil_Twilight , y=`Precipitation(in)`))

p7 <-ggplot(accidents) + geom_boxplot(aes(x= Nautical_Twilight , y=`Precipitation(in)`))

p8 <- ggplot(accidents) + geom_boxplot(aes(x= Astronomical_Twilight , y=`Precipitation(in)`))

p9 <- ggplot(accidents) + geom_boxplot(aes(x= Amenity , y=`Precipitation(in)`))

p10 <- ggplot(accidents) + geom_boxplot(aes(x= Crossing , y=`Precipitation(in)`))

p11 <- ggplot(accidents) + geom_boxplot(aes(x= Junction , y=`Precipitation(in)`))

p12 <- ggplot(accidents) + geom_boxplot(aes(x= Railway , y=`Precipitation(in)`))

p13 <- ggplot(accidents) + geom_boxplot(aes(x= Station , y=`Precipitation(in)`))

p14 <- ggplot(accidents) + geom_boxplot(aes(x= Stop , y=`Precipitation(in)`))

p15 <- ggplot(accidents) + geom_boxplot(aes(x= Traffic_Signal , y=`Precipitation(in)`))

grid.arrange(p1,p2,nrow = 2,top='Precipitation(in) vs Accidents categories')
grid.arrange(p3,p4,p5,p6,p7,p8,nrow = 3,top='Precipitation(in) vs Weather categories')
grid.arrange(p9,p10,p11,p12,p13,p14,p15,nrow = 4,top='Precipitation(in) vs Road categories')
```

## Check the correlation for Sunrise_Sunset,Civil_Twilight,Nautical_Twilight,Astronomical_Twilight

```{r}
library(lsr)

df = accidents %>%
  select(Sunrise_Sunset,Civil_Twilight,Nautical_Twilight,Astronomical_Twilight)

# function to get chi square p value and Cramers V
f = function(x,y) {
    tbl = df %>% select(x,y) %>% table()
    chisq_pval = round(chisq.test(tbl)$p.value, 4)
    cramV = round(cramersV(tbl), 4) 
    data.frame(x, y, chisq_pval, cramV) }

# create unique combinations of column names
df_comb = data.frame(t(combn(sort(names(df)), 2)), stringsAsFactors = F)

# apply function to each variable combination
df_res = map2_df(df_comb$X1, df_comb$X2, f)

# plot results
df_res %>%
  ggplot(aes(x,y,fill=chisq_pval))+
  geom_tile()+
  geom_text(aes(x,y,label=cramV))+
  scale_fill_gradient(low="red", high="yellow")+
  theme_classic()
```

